Clustering of Last.fm Music

### 2015-05-06 writeup/MSDgroupwriteup.tex
MF function
added ref notes

\section{Appendix}
\href{https://github.com/eringrand/musicanalysis}{Link to our github repository} 
\href{http://www.dtic.upf.edu/~ocelma/MusicRecommendationDataset/}{Link to the data set}

>>>>

To Reference a paper: 
The Million Song Dataset Challenge: \cite{McFee:2012:MSD:2187980.2188222} \\
Million Song Dataset Recommendation Project Report: \cite{li2012million} \\
codebook-based scalable music tagging with poisson matrix factorization: \cite{liangcodebook} \\
Matrix Factorization Techniques for Recommender Systems: \cite{koren2009matrix} \\
A Preliminary Study on a Recommender System for the Million Songs Dataset Challenge: \cite{aiolli2013preliminary} \\

\bibliography{msdref}

\section{Appendix}
\href{https://github.com/eringrand/musicanalysis}{Link to our github repository}
